### 2017-11-21 manuscript.rmd
bracts PP density map

###SIMMAP BRACTS:
```{r bracts, echo=F, fig.height=7, fig.width=12, message=F, warning=F}
#Simmap bracts
plotTree(ultratree, lwd = 4)
#plot(bract_sim_plot[2])
colors = c("black", "red")
names(colors) = c("Absent","Present")
bracts_sim %>% plotSimmap(lwd = 4, add = T, colors=colors) -> bract_sim_plot
nodelabels(pie=(describe.simmap(bracts_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

>>>>

###SIMMAP BRACTS:
```{r bracts, echo=F, message=F, warning=F}
#Simmap bracts
plotTree(ultratree, lwd = 4)
#plot(bract_sim_plot[2])
colors = c("black", "red")
names(colors) = c("Absent","Present")
bracts_sim %>% plotSimmap(lwd = 4, add = T, colors=colors) -> bract_sim_plot
nodelabels(pie=(describe.simmap(bracts_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(bracts_sim)
```
